---
title: "jstadden_6"
author: "Jared Stadden"
date: "10/18/2020"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Installing and loading packages:
```{r}
#install.packages("lpSolveAPI")
library(lpSolveAPI)
```

Reading lp file:

```{r}
lprec <- read.lp("jstadden_6.lp")
lprec
```
Because the supply does not equal the demand as required by the transportation problem, dummy variables were introduced (an imaginary Warehouse 4) so that we can achieve a feasible solution.

Solving lp:
```{r}
solve(lprec)
```
Value of 0 means solution was found

Objective value:
```{r}
get.objective(lprec)
```
The minimum combined cost of production and shipping is $132,790  

Decision variable values:
```{r}
get.variables(lprec)
```
x11 = 0  
x12 = 60  
x13 = 40  
x21 = 80  
x22 = 0  
x23 = 30  
*the dummy variables don't actually get produced:  
x14 = 0  
x24 = 10  
  
To minimize combined costs:    
Plant A should produce x11 + x12 + x13 = 100 AEDs  
Plant B should produce x21 + x22 + x23 = 110 AEDs  
Warehouse 1 should receive x11 + x21 = 80 AEDs  
Warehouse 2 should receive x12 + x22 = 60 AEDs  
Warehouse 3 should receive x13 + x23 = 70 AEDs  
  
  
  
Constraint RHS values:
```{r}
get.constraints(lprec)
```

