---
title: "Assignment 4"
author: "Jared Stadden"
date: "10/3/2020"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Installing and loading packages:
```{r}
#install.packages("lpSolveAPI")
library(lpSolveAPI)
```

Reading lp file:

```{r}
lprec <- read.lp("jstadden_4.lp")
lprec
```

Solving lp:
```{r}
solve(lprec)
```
Value of 0 means solution was found

Objective value:
```{r}
get.objective(lprec)
```
The max value found for the objective function was 696,000

Decision variable values:
```{r}
get.variables(lprec)
```
Small units produced at plant 1:
x1 = 0;  
Small units produced at plant 2:
x2 = 166.67;  
Small units produced at plant 3:
x3 = 416.67;  
Medium units produced at plant 1:
y1 = 177.78;  
Medium units produced at plant 2:
y2 = 666.67;  
Medium units produced at plant 3:
y3 = 0;  
Large units produced at plant 1:
z1 = 516.67;  
Large units produced at plant 2:
z2 = 0;  
Large units produced at plant 3:
z3 = 0;  


Constraint RHS values:
```{r}
get.constraints(lprec)
```
694.44 <= 750;  
833.33 <= 900;  
416.67 <= 450;  
13,000 <= 13,000;  
12,000 <= 12,000;  
5,000 <= 5,000;  
583.33 <= 750;  
844.44 <= 1,200;  
516.67 <= 900;  
(Last two zeros are for the equaivalent percentage contraints)
